Manuscript Figures for Genome Biology

### 2018-08-30 manuscript_figures/manuscript_figures.Rmd
Consider 0 -> 0 as zero change in infCov heatmaps (previously NA)

dftab <- left_join(inftab, uninftab, by = "id") %>%
  dplyr::mutate(diff_inf = nrejects - uninf) %>%
  dplyr::mutate(diff_inf_percent = diff_inf / nrejects) %>%
  dplyr::mutate(method = factor(method, levels = rowOrder)) %>%
  dplyr::group_by(casestudy, cov) %>%
  complete(method, dataset)

@@

>>>>

# calculate percentage diff as percentage of the smallest (nonzero) number 
# of rejections (i.e. using n rejects with informative or uninf for denominator,
# depending on which one was smaller while still being greater than zero)
dftab <- left_join(inftab, uninftab, by = "id") %>%
  dplyr::mutate(diff_inf = nrejects - uninf) %>%
  dplyr::mutate(basenum = ifelse(nrejects == 0 | uninf == 0, 
                                 pmax(nrejects, uninf),
                                 pmin(nrejects, uninf))) %>%
  dplyr::mutate(diff_inf_percent = diff_inf / basenum) %>%
  dplyr::mutate(method = factor(method, levels = rowOrder)) %>%
  dplyr::group_by(casestudy, cov) %>%
  complete(method, dataset)

@@

# if no change, set diff_inf_percent to zero, even if no rejections in either case
dftab <- dftab %>% 
  mutate(diff_inf_percent = ifelse(nrejects == uninf, 0, diff_inf_percent))
